D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-03 ootavacuous.tex
Add JMM Causality Test Cases 6-8.
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Listing~\ref{lst:Causality Test Case 1}
shows causality test case 1, for which the \co{r1 == r2 == 1} result
is to be allowed.
However, the herd7 tool does not find this litmus test's OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 2}
shows causality test case 2, for which the \co{r1 == r2 == r3 == 1} result
is to be allowed.
The herd7 tool finds this OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 3}
shows causality test case 3, for which the \co{r1 == r2 == r3 == 1} result
is to be allowed.
The herd7 tool finds this OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 4}
shows causality test case 4, for which the \co{r1 == r2 == 1} result
is to be forbidden.
The herd7 tool finds this OOTA cycle, but flags it as such using \co{S08}.

@@

Listing~\ref{lst:Causality Test Case 5}
shows causality test case 5, for which the \co{r1 == r2 == 1 && r3 == 0}
result is to be forbidden.
The herd7 tool finds this OOTA cycle, but flags it as such using \co{S08}.

@@

>>>>

Listing~\ref{lst:Causality Test Case 1}
shows causality test case 1, for which the \co{r1 == r2 == 1} result
is to be allowed.
However, the herd7 tool does not find this litmus test's cycle, presumably
because this tool does not do the deep inter-thread compiler analysis
required to find it.

@@

Listing~\ref{lst:Causality Test Case 2}
shows causality test case 2, for which the \co{r1 == r2 == r3 == 1} result
is to be allowed.
The herd7 tool finds this cycle, and does not flag it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 3}
shows causality test case 3, for which the \co{r1 == r2 == r3 == 1} result
is to be allowed.
The herd7 tool finds this cycle, and does not flag it as an OOTA cycle.

@@

Listing~\ref{lst:Causality Test Case 4}
shows causality test case 4, for which the \co{r1 == r2 == 1} result
is to be forbidden.
The herd7 tool finds this OOTA cycle, and flags it as such using \co{S8}.

@@

Listing~\ref{lst:Causality Test Case 5}
shows causality test case 5, for which the \co{r1 == r2 == 1 && r3 == 0}
result is to be forbidden.
The herd7 tool finds this OOTA cycle, and flags it as such using \co{S8}.

@@

\subsubsection{Causality Test Case 6}
\label{app:Causality Test Case 6}

Listing~\ref{lst:Causality Test Case 6}
shows causality test case 6, for which the \co{r1 == r2 == 1}
result is to be allowed.
The herd7 tool finds this cycle, and does not flag it as an OOTA cycle.

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-6.litmus @@
\end{verbatim}
\caption{Causality Test Case 6}
\label{lst:Causality Test Case 6}
\end{listing}

\subsubsection{Causality Test Case 7}
\label{app:Causality Test Case 7}

Listing~\ref{lst:Causality Test Case 7}
shows causality test case 7, for which the \co{r1 == r2 == r3 == 1}
result is to be allowed.
The herd7 tool finds this cycle, and does not flag it as an OOTA cycle.

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-7.litmus @@
\end{verbatim}
\caption{Causality Test Case 7}
\label{lst:Causality Test Case 7}
\end{listing}

\subsubsection{Causality Test Case 8}
\label{app:Causality Test Case 8}

Listing~\ref{lst:Causality Test Case 8}
shows causality test case 8, for which the \co{r1 == r2 == 1}
result is to be allowed.
The herd7 tool does not find this cycle, but when \co{r2} is explicitly
initialized to the constant \co{1}, it does find the cycle and refrains
from flagging it as an OOTA cycle.

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-8.litmus @@
\end{verbatim}
\caption{Causality Test Case 8}
\label{lst:Causality Test Case 8}
\end{listing}
